\thetitle

### 2020-11-20 sun_phases/spin_qudit_tomo.tex
minor notation change

In principle, maximizing the reconstruction error in Eq.~\eqref{eq:error_SM} over all qudit states $\rho$ would provide a tight upper bound on reconstruction error for any set of axes $V$.
To simplify this task somewhat, we first maximize Eq.~\eqref{eq:error_SM} over all $\rho$ with $\tr\p\rho=1$: this maximum occurs at a ``state'' $\rho_V^\star$ whose components are defined by
\begin{align}
  \ket{\rho_{V\ell}^\star} \stackrel{\ell\ne0}{\equiv}
  \f12 \N_{V\ell}^{-1} \ket{\chi_{V\ell}},
  &&
  \ket{\rho_{V,0}^\star} \equiv \f1{\sqrt{d}} \ket{0}.
\end{align}
The corresponding maximum of $\E_V$ is given by
\begin{align}
  \E_V\p{\rho_V^\star}^2 = \f1n \sum_{\ell>0}
  \sp{\f14 \bk{\chi_{V\ell}|\N_{V\ell}^{-1}|\chi_{V\ell}}
  - \f1d \tr\p{\N_{V\ell}}},
\end{align}
where the $\tr\p{\N_{V\ell}}$ terms above come from simplifying the $\ell=0$ terms of Eq.~\eqref{eq:error_SM} with $\rho\to\rho_V^\star$.
While $\E_V\p{\rho_V^\star}^2$ is a strict upper bound on $\E_V\p{\rho}^2$ over all $\rho$ with $\tr\p{\rho}=1$, this bound turns out to be useless in practice, because $\rho_V^\star$ will generally be a non-physical ``state'' with negative eigenvalues.
To find tight bound on $\E_V\p{\rho}^2$ over the space of physical qudit states $\rho$, we also need to constrain $\rho$ to have no negative eigenvalues.
Equipped with $\rho_V^\star$ and $\E_V\p{\rho_V^\star}^2$, we can expand
\begin{align}
  \E_V\p{\rho}^2 = \E_V\p{\rho_V^\star}^2
  - \f1n D_V\p{\rho,\rho_V^\star}^2,
  &&
  D_V\p{X,Y}^2 \equiv
  \sum_\ell \bk{\p{X-Y}_\ell | \N_{V\ell} | \p{X-Y}_\ell},
\end{align}
where $Z_\ell\equiv\sum_m \obk{T_{\ell m}|Z} \ket{m}$ is a vector of the degree-$\ell$ components of $Z$ in the polarization operator basis.
Finding the maximum of $\E_V$ over all qudit states $\rho$ thus amounts to finding the closest physical qudit state $\rho$ to $\rho_V^\star$, with distance measured by the metric $D_V$ induced by the noise matrices $\N_{V\ell}$.
This minimization problem is essentially solved for the case of $\N_{V\ell}=1$ in Ref.~\cite{smolin2012efficient}, but it is not obvious how to minimize $D_V\p{\rho,\rho_V^\star}^2$ for general $\N_{V\ell}$.
We leave the general problem of minimizing $D_V\p{\rho,\rho_V^\star}$ to future work, noting that this task may be assisted by the positivity conditions derived in Ref.~\cite{kryszewski2006positivity}.
A loose upper bound, which may nonetheless be tighter than that in Eq.~\eqref{eq:bound} of the main text (derived in Appendix \ref{sec:improved_bound}), might be found by the fact that physical qudit states $\rho$ satisfy $\obk{\rho|\rho}\le1$.

>>>>

In principle, maximizing the reconstruction error in Eq.~\eqref{eq:error_SM} over all qudit states $\rho$ would provide a tight upper bound on reconstruction error for any set of axes $V$.
To simplify this task somewhat, we first maximize Eq.~\eqref{eq:error_SM} over all $\rho$ with $\tr\p\rho=1$: this maximum occurs at a ``state'' $\sigma_V^\star$ whose components are defined by
\begin{align}
  \ket{\sigma_{V\ell}^\star} \stackrel{\ell\ne0}{\equiv}
  \f12 \N_{V\ell}^{-1} \ket{\chi_{V\ell}},
  &&
  \ket{\sigma_{V,0}^\star} \equiv \f1{\sqrt{d}} \ket{0}.
\end{align}
The corresponding maximum of $\E_V$ is given by
\begin{align}
  \E_V\p{\sigma_V^\star}^2 = \f1n \sum_{\ell>0}
  \sp{\f14 \bk{\chi_{V\ell}|\N_{V\ell}^{-1}|\chi_{V\ell}}
  - \f1d \tr\p{\N_{V\ell}}},
\end{align}
where the $\tr\p{\N_{V\ell}}$ terms above come from simplifying the $\ell=0$ terms of Eq.~\eqref{eq:error_SM} with $\rho\to\sigma_V^\star$.
While $\E_V\p{\sigma_V^\star}^2$ is a strict upper bound on $\E_V\p{\rho}^2$ over all $\rho$ with $\tr\p{\rho}=1$, this bound turns out to be useless in practice, because $\sigma_V^\star$ will generally be a non-physical ``state'' with negative eigenvalues.
To find tight bound on $\E_V\p{\rho}^2$ over the space of physical qudit states $\rho$, we also need to constrain $\rho$ to have no negative eigenvalues.
Equipped with $\sigma_V^\star$ and $\E_V\p{\sigma_V^\star}^2$, we can expand
\begin{align}
  \E_V\p{\rho}^2 = \E_V\p{\sigma_V^\star}^2
  - \f1n D_V\p{\rho,\sigma_V^\star}^2,
  &&
  D_V\p{X,Y}^2 \equiv
  \sum_\ell \bk{\p{X-Y}_\ell | \N_{V\ell} | \p{X-Y}_\ell},
\end{align}
where $Z_\ell\equiv\sum_m \obk{T_{\ell m}|Z} \ket{m}$ is a vector of the degree-$\ell$ components of $Z$ in the polarization operator basis.
Finding the maximum of $\E_V$ over all qudit states $\rho$ thus amounts to finding the closest physical qudit state $\rho$ to $\sigma_V^\star$, with distance measured by the metric $D_V$ induced by the noise matrices $\N_{V\ell}$.
This minimization problem is essentially solved for the case of $\N_{V\ell}=1$ in Ref.~\cite{smolin2012efficient}, but it is not obvious how to minimize $D_V\p{\rho,\sigma_V^\star}^2$ for general $\N_{V\ell}$.
We leave the general problem of minimizing $D_V\p{\rho,\sigma_V^\star}$ to future work, noting that this task may be assisted by the positivity conditions derived in Ref.~\cite{kryszewski2006positivity}.
A loose upper bound, which may nonetheless be tighter than that in Eq.~\eqref{eq:bound} of the main text (derived in Appendix \ref{sec:improved_bound}), might be found by the fact that physical qudit states $\rho$ satisfy $\obk{\rho|\rho}\le1$.
